%----------------------------------------------------------------------------------------
%	PACKAGES AND DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
% !TEX root=main.tex
\documentclass[10pt,a4paper]{article}

\addtolength{\oddsidemargin}{-.5in}
\addtolength{\evensidemargin}{-.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

% Graphics
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\graphicspath{{figures/}}

% Math
\usepackage{amssymb}
\usepackage{amsmath}

% Other
\usepackage{algorithmic}
\usepackage{array}
\usepackage{lipsum}
\usepackage{hyperref}
\usepackage[acronym]{glossaries}
\usepackage{url}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\setlength{\parindent}{12pt}

\providecommand{\keywords}[1]
{
  \small	
  \textbf{\textit{Keywords---}} #1
}

%----------------------------------------------------------------------------------------
% Acronyms
%----------------------------------------------------------------------------------------
\newacronym{adc}{ADC}{Analog-Digital Converter}
\newacronym{daq}{DAQ}{Data Acquisition}
\newacronym{dc}{DC}{Direct Current}
\newacronym{diy}{DIY}{Do It Yourself}
\newacronym{i2c}{I2C}{Inter-Integrated Circuit}
\newacronym{iaq}{IAQ}{Indoor Air Quality}
\newacronym{icsp}{ICSP}{In-Circuit Serial Programming}
\newacronym{iir}{IIR}{Infinite Impulse Response}
\newacronym{lfn}{LFN}{Low-Frequency Noise}
\newacronym{lpg}{LPG}{Liquefied Petroleum Gas}
\newacronym{pcb}{PCB}{Printed Circuit Board}
\newacronym{psd}{PSD}{Power Spectral Density}
\newacronym{pwm}{PWM}{Pulse-Width Modulation}
\newacronym{spi}{SPI}{Serial Peripheral Interface}
\newacronym{usb}{USB}{Universal Serial Bus}
\newacronym{twi}{TWI}{Two Wire Interface}


%----------------------------------------------------------------------------------------
% MAIN PART
%----------------------------------------------------------------------------------------
\begin{document}

\title{Data Acquisition System for Indoor Air Quality Monitoring using Arduino UNO R3 Board}
\author{Erick Andrés Obregón Fonseca}
\date{\today}
\maketitle




%----------------------------------------------------------------------------------------
% Abstract
%----------------------------------------------------------------------------------------
\begin{abstract}
\normalsize
In recent years, scientists, politicians, and environmental institutions have focused on Indoor Air Quality. Later research has demonstrated that poor air quality can lead to different respiratory problems and cardiovascular diseases. This project aims to develop a prototype for an Indoor Air Quality Monitoring System using an Arduino UNO board. For such a task, variables like temperature, humidity, and gas concentrations are measured to detect any condition that can cause long-term health issues. First, some basic concepts are introduced. Then, the following methodology is described, where the development of the system is shown. This includes the choice of sensor, design of amplification, and filtering stages for analog sensor, and the proposed algorithm for data sampling. Finally, the results and conclusions are discussed regarding the design of the conditioning and filtering stage of the analog sensor.
\end{abstract}

%----------------------------------------------------------------------------------------
% Keywords
%----------------------------------------------------------------------------------------
\keywords{Arduino UNO, DAQ system, I2C, IQA, sensors}

%----------------------------------------------------------------------------------------
% Table of Content
%----------------------------------------------------------------------------------------
\setcounter{tocdepth}{2}
\tableofcontents


\clearpage

%----------------------------------------------------------------------------------------
% Main Part
%----------------------------------------------------------------------------------------
\input{sections/01-introduction}
\input{sections/02-methodology}
\input{sections/03-results_and_discussion}
\input{sections/04-conclusions}

\clearpage

%----------------------------------------------------------------------------------------
% Bibliography
%----------------------------------------------------------------------------------------
\clearpage
\bibliography{bibliography/sample}{}
\bibliographystyle{ieeetr}

\end{document}
