\section{Conclusion}
\label{sec:conclusion}
\hspace{8pt}
In this report, I presented an IAQ monitor which is important for keeping people's health and notifying them when the air quality can be long-term harmful. \\

\acrshort{daq} systems are designed to collect, measure, and process data from various sensors, including analog, digital, and other connected for any data transmission protocol like SPI and I2C. They play an important role in monitoring and controlling systems with different applications. Signals acquired from sensors are vulnerable to different kinds of noise that can affect the measurement and lead to errors. It is also important to condition the analog signal to meet the ADC requirements. \\

Filtering the signals helps to clean the possible noise that they can bring to the system. Bessel filters provide a maximally flat response with minimal ripple, unlike other filters like Butterworth or Chebyshev. This aided by its characteristics of preserving phase accuracy and minimizing signal quality loss, makes it ideal for applications where these features are critical. \\

The operational amplifiers have different parameters that need to be taken into consideration to choose the right model for the application. Low power consumption is important in those systems that are battery-based and will be stand-alone for long times. Low offset voltage helps to improve the precision of the output, by minimizing the voltage difference between its terminal when output is zero. \\

Designing a \acrshort{daq} system can be time-intensive. Using tools like Texas Instruments Filter Design Tool can help to minimize the time of the design development and reduce the human error during value calculation.


